### 2012-04-17 trunk/ijcis-pos-model/sources/temporalModel.tex
updated version

\begin{definiton}
\label{def:generalized-fuzzy-domain}
$D$ is the discourse domain, $\tilde \Pow\left(D \right)$ is the set of all possibility distributions defined on $\D$, plus the NULL constant. The generalized fuzzy domain $D_G$ is defined as:
\begin{equation}
\label{eq:generalized-fuzzy-domain}
D_G \subseteq \tilde \Pow\left(D \right)\cup \text{NULL}
\end{equation}
\end{definition}

@@

Note that $\T_G \subseteq D_G$.

>>>>

\begin{definition}
\label{def:generalized-fuzzy-domain}
$D$ is the discourse domain, $\tilde \Pow\left(D \right)$ is the set of all possibility distributions defined on $D$, plus the NULL constant. The generalized fuzzy domain $D_G$ is defined as:
\begin{equation}
\label{eq:generalized-fuzzy-domain}
D_G \subseteq \tilde \Pow\left(D \right)\cup \text{NULL}
\end{equation}
\end{definition}
The datatypes for $D_G$ are shown in table \ref{tablaaaaaaaaa}
\textcolor{red}{poner tabla}

@@

Note that $\T_G \subseteq D_G$. The datatypes for this domain have been studied previously in section \ref{sec:time-rep} and are shown in tables \ref{tbl:time-point-types},\ref{tbl:time-interval-types}.

\begin{definition}
A generalized fuzzy temporal relation $R_{FTG}$ is given by:
\label{def:generalized-fuzzy-temporal-relation}
\begin{equation}
\label{eq:generalized-fuzzy-temporal-relation}
R_{FTG} = \left(\Head, \Body \right)
\end{equation}
Where $\Head$ is the Head of the relation and consist on a fixed set of triplets attribute- domain - compatibility with an optional the valid-time attribute:

\begin{align}
\label{eq:head-valid-time}
\Head = \big \lbrace \left(A_{G1}:D_{G1}\left[,C_{A_{G1}} \right] \right),\\
\nonumber
 \ldots,\\
 \nonumber
  \left(A_{Gn}:D_{Gn}\left[,C_{A_{Gn}} \right] \right),\\
  \nonumber
  \Big[  \left( \text{PVP}, D_{\text{PVP}}\left[,C_{A_{\text{PVP}}} \right] \right) \Big] \big \rbrace
\end{align}
Note that $D_{Gj}$ ($j = 1, \ldots, n$) is the domain for the attribute $A_{Gj}$. $C_{A_{Gj}}$ is the compatibility attribute in the unit interval $\left[0, 1 \right]$.

$\Body$ is the body of the relation and it consists on a set of tuples. Each tuple is a triplet attribute- value- degree with an optional valid-time attribute:

\begin{align}
\label{eq:body-valid-time}
\Body = \big \lbrace \left(A_{G1}:\tilde{d}_{i1}\left[,c_{i1} \right] \right),\\
\nonumber
 \ldots,\\
 \nonumber
  \left(A_{Gn}:\tilde{d}_{in}\left[,c_{in} \right] \right),\\
  \nonumber
   \Big[  \left( \text{PVP}, \tilde{d}_{\text{PVP}} \left[,C_{A_{\text{PVP}}} \right] \right)  \Big] \big \rbrace
\end{align}

\end{definition}

The definition in \cite{Medina1994} for $R_{FTG}$ shows that classical relations are a particular case of this model.

\begin{definition}
\label{def:value-component}
The value component $R^{v}_{FTG}$ of a fuzzy temporal relation $R_{FTG}$ is a set with the value components for both the head and the body of the relation:
\begin{align}
\label{eq:value-component}
R^{v}_{FTG} = \left \lbrace \Head^{v},\Body^{v} \right \rbrace \\
\nonumber
\text{Where: } \\
\nonumber
\Head^{v} = \left \lbrace A_{G1}:D_{G1}, \ldots,  A_{Gn}:D_{Gn} \right \rbrace \\
\nonumber
\Body^ {v} = \left \lbrace A_{G1}:\tilde{d}_{i1}, \ldots,  A_{Gn}:\tilde{d}_{in}\ \right \rbrace \\
\end{align}
\end{definition}

\begin{definition}
\label{def:compatibility-component}
The compatibility component $R^{c}_{FTG}$ of a fuzzy temporal relation $R_{FTG}$ is a set with the compatibility components for both the head and the body of the relation:
\begin{align}
\label{eq:compatibility-component}
R^{c}_{FTG} = \left \lbrace \Head^{c},\Body^{c} \right \rbrace \\
\nonumber
\text{Where: } \\
\nonumber
\Head^{c} = \left \lbrace \left[C_{A_{G1}} \right], \ldots,  \left[C_{A_{Gn}} \right] \right \rbrace \\
\nonumber
\Body^ {c} = \left \lbrace \left[ c_{i1} \right], \ldots, \left[ c_{in} \right] \right \rbrace \\
\end{align}
\end{definition}

\begin{definition}
\label{def:temporal-component}
The temporal component $R^{t}_{FTG}$ of a fuzzy temporal relation $R_{FTG}$ is a set with the temporal components for both the head and the body of the relation:
\begin{align}
\label{eq:temporal-component}
R^{t}_{FTG} = \left \lbrace \Head^{t},\Body^{t} \right \rbrace \\
\nonumber
\text{Where: } \\
\nonumber
\Head^{t} = \left \lbrace \left( \text{PVP}, D_{\text{PVP}}\left[,C_{A_{\text{PVP}}} \right] \right) \right \rbrace \\
\nonumber
\Body^ {t} = \left \lbrace  \left[ \text{PVP}, \tilde{d}_{\text{PVP}} \left[,C_{A_{\text{PVP}}} \right] \right]  \right \rbrace \\
\end{align}
\end{definition}

Analogously, it is possible to define the the value component for the temporal part and the compatibility component for the temporal part.

\begin{definition}
\label{def:generalized-primary-key}
A generalized primary key, $K_G$ is a subset of the head:
\begin{align}
\label{eq:generalized-primary-key}
K_G \subseteq \Head, K_G = \left \lbrace  \left(A_{Gs}:D_{Gs} \right) \right \rbrace \\
\nonumber
s\in S \subseteq \left(1, \ldots, n \right) \\
\nonumber
\forall s \in S, \text{Typeof } \left(D_{Gs} \right) \in \left \lbrace 1, 2 \right \rbrace \\
\nonumber
\forall i, i' \in \left \lbrace 1, \ldots, m\right \rbrace , \exists s \in S: \left(A_{Gs}:d_{is} \right) \neq \left(A_{Gs}:d_{i's} \right)
\end{align}
\end{definition}

\texcolor{red}{primary temporal key}

\begin{definiton}
\label{def:generalized-fuzzy-temporal-key}
A generalized fuzzy temporal key, $K_{GT}$ is a subset od the head:

\end{definition}
